Systemic risk and contagion effects in Australian financial institutions and sectors

### 2015-05-29 old stuff/obs.tex
pdj initial

\section{Weihao's approach}

@@

>>>>

\section{Bivariate case}

@@

\subsection{Copula stressors}

\newcommand{\Es}{\E_\phi}

Stressing can be based on a vector of variables $x$ with distribution $F(x)=u$.   Given a copula $\Phi(u)$ with density $\phi(u)$ consider
the stressed expectation 
\be{copula}
\Es(p_{it}) \equiv \int \E(p_{it}|x)  \de\Phi\{F(x)\}  =  \E\{\phi(u)\E(p_{it}|x)\}  \ ,
\ee
The  copula $\Phi(u)$ is designed to magnify  stressful situations such as  where all components of $x$ are abnormally low.
If $\Phi(u)=u$ then $\phi(u)=1$ and $\Es(p_{it})=\E(p_{it})$.

For example $\Phi\{F(x)\}$ may have stronger tail dependence than $F$.   In the extreme  $\Phi(u)=\min_i(u_i)$ making all  variables in $x$  comonotonic.   The copula $\Phi(u)$  leaves marginals intact and acts as a stressor on the copula  $c(u)$  corresponding to $F$ since
$$
\de\Phi\{F(x)\} = \phi(u)c(u)\prod_if_i(x_i)\ ,
$$
where the $f_i$ are the  marginal densities of $F$.   Further marginal stress is induced by allowing $\Phi(u)$ to have non--uniform marginals in which case
$$
\de \Phi(u) = \phi(u)\prod_i\phi_i(u_i)\de u\ ,
$$
where $\phi(u)$ has, as before, uniform marginals and the $\phi_i(u_i)\ge 0$ induce non--uniformity in each of the marginals subject to $\E\{\phi_i(u_i)\} = 1$.
